---
title: "Working with dates"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{working-with-dates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette teaches you how makeup can help you when working with date values. 

```{r setup}
library(makeup)
```

### Working with samples

One of the principal makeup argument is `sample =`. In it you can set the output date format as you need for your project.

```{r}
date_value <- as.Date("2020-03-04")

# Example 1
makeup(v = date_value,
       sample = "Junio 4 de 2011")


# Example 2
makeup(v = date_value, 
           sample = "Junio 4 2011")


# Example 3
makeup(v = date_value, 
       sample = "4 de junio de 2011")
```

### Working with locale

makeup also supports a wide variety of output format languages by setting `locale = ` argument from one of the package `available_locales`:
```{r}
available_locales
```
So, setting the locale argument makeup can work like this:
```{r}
# Example 1 - Colombia
makeup(v = date_value, 
       locale = "es-CO")


# Example 2 - Deutsch - Deutschland
makeup(v = date_value, 
       locale = "de-DE")


# Example 3 - English-USA
makeup(v = date_value, 
       locale = "en-US")


# Example 4 - Frenc - France
makeup(v = date_value, 
       locale = "fr-FR")


# Example 5 - Portuguese - Brazil
makeup(v = date_value, 
       locale = "pt-BR")
```

### Working with format

You can set the output with a particular date `format`. For example, if you need something like: _"March 04 2020"_ you'll have to set the following combination:

- **%B** --> _Unabbreviated month_

- **%d** --> _Day as a number_

- **%Y** --> _4-digit year_


and with makeup you can:
```{r}
# Example 1: format = "%B %d %Y"

makeup(v = date_value,
       format = "%B %d %Y")
```

